Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-08-28 Documents/Paper/ms.tex
Attempt at a conclusion

\subsection{Results}
The results from running DNS on the simulated galaxy data are shown in
Figures~\ref{fig:galaxyfield_likelihood} and~\ref{fig:N_galaxy_result}.
This problem, like the sinusoidal problem, exhibits a phase transition, which
can be seen in Figure~\ref{fig:galaxyfield_likelihood}. The phase transition
separates models which only fit the brightest galaxies from models that
also fit the faint galaxies close to the noise level. This phase transition
does not affect the posterior distribution, as the low-$N$ solutions are
eventually found to have very low importance.

@@

>>>>

\subsection{Results}
The results from running DNS on the simulated galaxy data are shown in
Figures~\ref{fig:galaxyfield_likelihood} and~\ref{fig:N_galaxy_result}.
This problem, like the sinusoidal problem, exhibits a phase transition, which
can be seen in Figure~\ref{fig:galaxyfield_likelihood}. The phase transition
separates models which only fit the brightest galaxies from models that
also fit the faint galaxies close to the noise level. This phase transition
does not affect the posterior distribution, as the low-$N$ solutions are
eventually found to have very low importance. However it would cause difficulty
for a thermal approach to calculating the marginal likelihood.

@@

\section{Conclusions}
In this paper, we presented a general approach to trans-dimensional Bayesian
inference problems. To compute the posterior distribution in these contexts,
birth and death MCMC moves are commonly used. However, the approach presented
here replaces the posterior distribution with the alternative target
distribution used in Diffusive Nested Sampling. This is done to facilitate
mixing between multiple modes, along strong dependencies,
and between different phases. Additionally,
the marginal likelihood can be computed including the sum over the unknown
number of components. The method was demonstrated on two illustrative examples
inspired by astronomical data analysis, but should be applicable in other
contexts such as mixture modelling. Software (in C++) implementing the
general Metropolis proposals for these models, as well as the specific
examples, is available at {\tt https://github.com/eggplantbren/RJObject}.
